### 2018-01-26 includes/problems.tex
small fix to transformed suite

    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
    Every problem in the suite is named according to its seed and the transformations it undertook. For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice, first by fuzz and then by graft. See Table~\ref{tbl:transformed} for an overview description of the suite.

    The suite is divided into two categories. The first category, labeled Amazon, started as two seed files.
    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
    \todo{Can I say that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
    In total, 516 unique problems were generated from these two seeds.

    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} \todo{Is this right? If so where we can cite?}. This test suite contains 42 problems dealing with a wide variety of regular expressions.
    Through accumulative transformations, as before, we were able to produce 10,577 unique benchmarks.

@@

>>>>

    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
    Every problem in the suite is named according to its seed and the transformations it undertook. 
    For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice:
    first by fuzz, and then by graft.

    The suite is divided into two categories. For an overview see Table~\ref{tbl:transformed}.

@@

    The first category, labeled Amazon, started as two seed files.
    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
    \todo{Can I say something like that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
    In total, 516 unique problems were generated from these two seeds.

    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} 
    \todo{Is this right? If so where we can cite?}. 
    This test suite contains 42 problems dealing with a wide variety of regular expressions.
    Through cumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
